---
title: "Homework 2"
author: "Weize Sun"
date: "10/6/2021"
output: github_document
---
```{r}
library(tidyverse)
```

## Problem 1

```{r}
trash_wheel_df = readxl::read_excel(
  "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
  sheet = "Mr. Trash Wheel",
  range = "A2:N534") %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(sports_balls = round(sports_balls))
```


```{r}
pre_19 = readxl::read_excel(
  "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
  sheet = "2019 Precipitation",
  range = "A2:B14") %>% 
  janitor::clean_names() %>% 
  drop_na(total) %>% 
  mutate(year = 2019) %>% 
  relocate(year)

pre_18 = readxl::read_excel(
  "./data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
  sheet = "2018 Precipitation",
  range = "A2:B14") %>% 
  janitor::clean_names() %>% 
  drop_na(total) %>% 
  mutate(year = 2018) %>% 
  relocate(year)

pre_1819 = full_join(pre_18, pre_19) %>% 
  mutate(month = month.name[month])

pre_1819
```

```{r}
sum(pull(pre_18, total))
ball_19 = filter(trash_wheel_df, year == 2019)
median(pull(ball_19, sports_balls))
```

** The observation of trash_wheel_df is 345 with 14 variables, and we are specifically paying attention to variable *sports_balls*. The observation of pre_1819 is 24, and we are specifically looking at variable *total*. For available data, the total precipitation in 2018 is 70.33, and the median number of sports balls in a dumpster in 2019 is 9. **



## Problem 2

```{r}
pols_month_df = read.csv("./data/fivethirtyeight_datasets/pols-month.csv") %>% 
  janitor::clean_names() %>% 
  separate(mon, into = c("year", "month", "day"), sep = "-") %>% 
  mutate(month = as.numeric(month)) %>%
  mutate(month = month.name[month]) %>% 
  rename(republic = prez_gop, democratic = prez_dem) %>% 
  pivot_longer(
    c(republic, democratic),
    names_to = "president",
    values_to = "number") %>% 
  filter(number != 0) %>% 
  select(-day, -number) 
```

```{r}
snp_df = read.csv("./data/fivethirtyeight_datasets/snp.csv") %>% 
  separate(date, into = c("month", "day", "year"), sep = "/") %>% 
  relocate(year, month) %>% 
  mutate(month = as.numeric(month)) %>% 
  mutate(month = month.name[month]) %>% 
  select(-day) 

snp_before_2000 = filter(snp_df, year >= 20) %>% 
  mutate(year = as.character(as.numeric(year) + 1900))
snp_after_2000 = filter(snp_df, year <= 20) %>% 
  mutate(year = as.character(as.numeric(year) + 2000))

snp_final = bind_rows(snp_before_2000, snp_after_2000)
```

```{r}
unemployment_df = read.csv("./data/fivethirtyeight_datasets/unemployment.csv") %>% 
  pivot_longer(
    Jan:Dec,
    names_to = "month",
    values_to = "unemployment"
  ) %>% 
  mutate(month = month.name[match(month,month.abb)]) %>% 
  rename(year = Year) %>% 
  mutate(year = as.character(year))
```

```{r}
pols_snp = left_join(pols_month_df, snp_final) 
final_df = left_join(pols_snp, unemployment_df)

final_df
```

```{r}
dim(pols_month_df)
range(pull(pols_month_df, year))
names(pols_month_df)

dim(snp_final)
range(pull(snp_final, year))
names(snp_final)

dim(unemployment_df)
range(pull(unemployment_df, year))
names(unemployment_df)

dim(final_df)
range(pull(final_df, year))
names(final_df)
```

**For pols_month_df, the dimension is (822 x 9), the range of year is (1947, 2015), and key variables is "president".**

**For snp_final, the dimension is (787 x 3), the range of year is (1950, 2015), and key variable is "close".**

**For unemployment_df, the dimension is (816 x 3), the range of year is (1948, 2015), and key variable is "unemployment".**

**For final_df, the dimension is (822 x 11), the range of year is (1947, 2015), and key variable is "president", "close", "unemployment".**



## Problem 3

```{r}
popular_baby_names_df = 
  read.csv("./data/Popular_Baby_Names (1).csv") %>% 
  janitor::clean_names() %>% 
  mutate(ethnicity = recode(ethnicity, "ASIAN AND PACI" = "ASIAN AND PACIFIC ISLANDER",
                            "BLACK NON HISP" = "BLACK NON HISPANIC",
                            "WHITE NON HISP" = "WHITE NON HISPANIC"),
        child_s_first_name = str_to_sentence(child_s_first_name),
        gender = str_to_sentence(gender),
        ethnicity = str_to_sentence(ethnicity))

nrow(popular_baby_names_df)
```

```{r}
popular_baby_names_df = 
  distinct(popular_baby_names_df, .keep_all= TRUE)

nrow(popular_baby_names_df)
```


```{r}
olivia_rank_df = 
  popular_baby_names_df %>%
  filter(child_s_first_name == "Olivia" & gender == "Female") %>%
  select(-gender, -child_s_first_name, -count) %>% 
  pivot_wider(
    names_from = year_of_birth,
    values_from = rank
  )

popular_male_name_df = 
  popular_baby_names_df %>%
  filter(gender == "Male" & rank == 1) %>% 
  select(-gender, -rank, -count) %>% 
  pivot_wider(
    names_from = year_of_birth,
    values_from = child_s_first_name
  )
```


```{r}
m_nonhis_2016 = 
  popular_baby_names_df %>% 
  filter(gender == "Male" & ethnicity == "White non hispanic" & year_of_birth == 2016)

ggplot(m_nonhis_2016, aes(x = rank, y = count)) +
  labs(title = "correlation between names of white non-hispanic male children and rank",
       x = "rank",
       y = "# of children") + geom_point()
```



